First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$

### 2020-02-06 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/body.tex
updated

The trigger setup for this experiment required a minimum of 3/4 hodoscope planes for data readout in each spectrometer. Due to the absence of significant background and the negligible
accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) measures was found to have little to no effect on the final cross section.\\

@@

\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo

@@

momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}.\\

@@

were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and
target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}. The values in parentheses were averaged over all data sets. \\

@@

of different data sets. For $\theta_{nq}= 35^{o}, 45^{o} and 75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.

@@

to the statistical uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\

@@

\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are well reproduced  by  all models when FSI are included.

@@

\indent Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and

@@

deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}.
\begin{figure}[h!]

@@

\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively.
Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSI are reduced.
At larger recoil momenta where the ratio is $R>1$ and increasing.  At $\theta_{nq}=35^{o}$ FSI start to dominate for missing moment above typically above 800 MeV/c for the CD-Bonn calculation
while the other models predict still relatively small FSI below 900 MeV/c. At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based
calculation above 600 MeV/c. \\
\indent Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small (<30\%).  This behavior of the data is new and 

>>>>

The trigger setup for this experiment required a minimum of 3/4 hodoscope planes to detect a signal for data readout in each spectrometer. Due to the absence of significant background and the low
accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section.\\

@@

\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo

@@

momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_phdthesis}.\\

@@

were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_phdthesis} and
target boiling factors ($4.2 \%$)\cite{cyero_phdthesis}. The values in parentheses were averaged over all data sets. \\

@@

of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.

@@

to the statistical uncertainty (25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\

@@

\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.

@@

\indent Beyond $p_{r}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and

@@

deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
region where recoil angles are small and FSI are reduced. \\
\indent At larger recoil momenta where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{o}$ FSI start to dominate for
missing momenta typically above 800 MeV/c for the CD-Bonn
\begin{figure}[t!]

@@

calculation while the other models predict still relatively small FSI below 900 MeV/c.
At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
\indent Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.  This behavior of the data is new

### 2020-02-06 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/introduction.tex
updated

GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$. This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$. Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ and, equivalently,  $\theta_{nq}\sim40^{o}$ is the preferred choice to suppress IC as well as FSI. \\

>>>>

GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$. This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$. Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI. \\
